Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

@@

>>>>

It is shown that metrics like PESQ, SI-SNR, STOI do not reflect speech quality of output of 
vocoders due to the fact that the vocoder output does not focus strictly on frame alignment
\cite{tokensplit,selm}. To measure the speech quality, 
speech intelligibility, and speech similarity.  We have used

@@

\begin{center}
\begin{tabular}{ c c c }
    \hline
    cell1 & cell2 & cell3 \\ 
    \hline
    cell4 & cell5 & cell6 \\  
    cell7 & cell8 & cell9    
\end{tabular}
\end{center}
